Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-04-12 paper/manuscript.Rmd
switch to apa_table, less complicated way to count gender in sample characteristics

vali_kids <- vali %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

vali_kids_gender <- vali %>% 
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  filter(gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

vali_kids <- vali_kids %>% 
  left_join(vali_kids_gender, by = c("datacollection", "ageInYears"))

vali_adults <- vali %>%
  filter(ageInYears == 18) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
  )

vali_adults_gender <- vali %>% 
  filter(ageInYears == 18 & gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

vali_adults <- vali_adults %>% 
  full_join(vali_adults_gender, by = character())
```
## Participants
We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology. The in-person child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).

@@

reli_kids <- reli %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

reli_kids_gender <- reli %>% 
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  filter(gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

reli_kids <- reli_kids %>% 
  left_join(reli_kids_gender, by = c("datacollection", "ageInYears"))

reli_adults <- reli %>%
  filter(ageInYears == 18) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
  )

reli_adults_gender <- reli %>% 
  filter(ageInYears == 18 & gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

reli_adults <- reli_adults %>% 
  full_join(reli_adults_gender, by = character())
```
## Participants
For our child sample, we went to kindergartens in Leipzig and surroundings.
The child sample consisted of 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).

@@

extvali_sample <- extvali %>%
  group_by(ageInYears) %>%
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
  )

extvali_gender <- extvali %>% 
  group_by(ageInYears) %>%
  filter(gender == "f") %>% 
  summarise(
    nFemales = length(unique(subjID))
  )

extvali_sample <- extvali_sample %>% 
  left_join(extvali_gender, by = c("ageInYears"))
```

@@

On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box. Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments. On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box. In all cases, however, ELPD difference scores were smaller than their standard errors. Similarly, 95% CI of the model estimates included zero and were rather wide. Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.

```{r webcam_coding}
webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds")

knitr::kable(webcam_models)
```

@@

#### WAIC scores and weights of the model comparison
As can be seen, ELPD difference scores are smaller than their respective standard errors. WAIC scores between models don't differ substantially. All effects except when a child entered childcare positively influence performance.

```{r extvali_results}
extvali_models <- readRDS(file = "../saves/extvali-results.rds")
knitr::kable(extvali_models)
```

>>>>

vali_kids <- vali %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )

vali_adults <- vali %>%
  filter(ageInYears == 18) %>% 
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)), 
    female = ifelse(gender == "f", 1, 0),
  ) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```
## Participants
We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig and surroundings that cooperate with the Max Planck Institute for Evolutionary Anthropology. The in-person child sample consisted of 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls),
`r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls),
and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, 
SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`
- `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, 
`r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).

@@

reli_kids <- reli %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
    nFemales = ceiling(sum(female/30)), # 15 test trials * 2
  )

reli_adults <- reli %>%
  filter(ageInYears == 18) %>% 
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)), 
    female = ifelse(gender == "f", 1, 0),
  ) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = sum(female),
  ) %>% 
  mutate(
    nFemales = ifelse(studyversion == "hedge", nFemales/60, nFemales/64), # test trials * 2
    nFemales = ceiling(nFemales)
  )
```
## Participants
For our child sample, we went to kindergartens in Leipzig and surroundings.
The child sample consisted of 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised"])` children, including 
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` 3-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "3"])` girls),
`r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` 4-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "4"])` girls),
and `r sum(reli_kids$nTotal[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` 5-year-olds 
(mean = `r sum(reli_kids$meanAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` months, 
SD = `r sum(reli_kids$sdAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
range = `r sum(reli_kids$minAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`
- `r sum(reli_kids$maxAgeInMonths[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])`, 
`r sum(reli_kids$nFemales[reli_kids$datacollection == "in-person - supervised" & reli_kids$ageInYears == "5"])` girls).

@@

extvali_sample <- extvali %>%
  group_by(ageInYears) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```

@@

On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box. Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments. On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box. In all cases, however, ELPD difference scores were smaller than their standard errors. Similarly, 95% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}). Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.

```{r webcam_table, results = "asis"}
webcam_models <- readRDS(file = "../saves/supplements-webcamcoding-results.rds") %>%
  mutate(across(c(waic, waic_weight, elpd_diff, se_diff), as.numeric)) %>% 
  mutate_if(is.numeric, round, 2)

papaja::apa_table(
  webcam_models, 
  caption = "Model comparison for exploratory webcam coding of parental interference", 
  note = "All models included random intercepts for participant and target position.", 
  escape = T
)
```

@@

#### WAIC scores and weights of the model comparison
As can be seen, ELPD difference scores are smaller than their respective standard errors. WAIC scores between models don't differ substantially (Table \ref{tab:extvali_table}). All effects except when a child entered childcare positively influence performance.

```{r extvali_table, results = "asis"}
extvali_models <- readRDS(file = "../saves/extvali-results.rds") %>% 
  mutate(across(c(waic, waic_weight, elpd_diff, se_diff), as.numeric)) %>% 
  mutate_if(is.numeric, round, 2)

papaja::apa_table(
  webcam_models, 
  caption = "Model comparison for influences of children's social surrounding", 
  note = "All models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants", 
  escape = T
)
```

### 2022-04-12 paper/manuscript.tex
switch to apa_table, less complicated way to count gender in sample characteristics

In addition, we recruited a remote adult sample by advertising the study on \emph{Prolific}. \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of 50, 50, 50, and 50 English-speakers with an average age of 31.92, 31.92, 30.76, and 30.76 years (SD = 12.15, 12.15, 9.12, and 9.12, range = 18, 18, 19, and 19 - 63, 63, 59, and 59, 36, 28, 36, and 28 females).
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour). \emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.

@@

For our child sample, we went to kindergartens in Leipzig and surroundings.
The child sample consisted of
106 children, including
35 3-year-olds
(mean = 42.57 months,
SD = 2.98,
range = 38
- 47,
17 girls),
38 4-year-olds
(mean = 53.77 months,
SD = 3.16,
range = 48
- 59,
19 girls),
and 33 5-year-olds
(mean = 66.12 months,
SD = 3.36,
range = 61
- 71,
17 girls).

The adult sample was recruited over \emph{Prolific} and consisted of 70, 70, 66, and 66 English-speakers with an average age of 25.43, 25.43, 26.05, and 26.05 years (SD = 6.43, 6.43, 9.44, and 9.44, range = 18, 18, 18, and 18 - 51, 51, 71, and 71, 45, 42, 45, and 42 females).

@@

For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
136 children, including
41 3-year-olds
(mean = 43.17 months,
SD = 3.13,
range = 37
- 47,
20 girls),
46 4-year-olds
(mean = 54.43 months,
SD = 2.76,
range = 48
- 59,
26 girls),
and 49 5-year-olds
(mean = 66.25 months,
SD = 3.47,
range = 60
- 71,
23 girls).

@@

On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box. Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments. On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box. In all cases, however, ELPD difference scores were smaller than their standard errors. Similarly, 95\% CI of the model estimates included zero and were rather wide. Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.

\begin{tabular}{l|r|r|r|r}
\hline
model & waic & waic\_weight & elpd\_diff & se\_diff\\
\hline
mPerTrialVerificationChoice & 263.24183 & 0.6469352 & 0.0000000 & 0.000000\\
\hline
mPerTrialNull & 263.74712 & 0.3530572 & -0.2526455 & 1.202097\\
\hline
mPerTrialPI & 264.34608 & 0.0000048 & -0.5521261 & 0.978696\\
\hline
mPerTrialRepeatedTestquestion & 265.43452 & 0.0000011 & -1.0963445 & 1.272427\\
\hline
mPerTrialHintsEyes & 265.67182 & 0.0000014 & -1.2149955 & 1.255888\\
\hline
mPerTrialParentSpeech & 266.45389 & 0.0000003 & -1.6060301 & 1.211500\\
\hline
mPerSubjectRepeatedTestquestion & 83.52517 & 0.7033000 & 0.0000000 & 0.000000\\
\hline
mPerSubjectPI & 88.25288 & 0.0000019 & -2.3638570 & 3.596520\\
\hline
mPerSubjectNull & 89.25650 & 0.0000003 & -2.8656662 & 3.608723\\
\hline
mPerSubjectVerificationChoice & 89.85833 & 0.2966959 & -3.1665822 & 4.484388\\
\hline
mPerSubjectParentSpeech & 90.44632 & 0.0000018 & -3.4605795 & 4.204938\\
\hline
mPerSubjectHintsEyes & 92.76122 & 0.0000001 & -4.6180264 & 3.773420\\
\hline
\end{tabular}

@@

As can be seen, ELPD difference scores are smaller than their respective standard errors. WAIC scores between models don't differ substantially. All effects except when a child entered childcare positively influence performance.

\begin{tabular}{l|r|r|r|r}
\hline
model & waic & waic\_weight & elpd\_diff & se\_diff\\
\hline
PE & 2390.222 & 0.5405439 & 0.0000000 & 0.0000000\\
\hline
siblingsVarietyScoreP & 2390.429 & 0.3408146 & -0.1032133 & 1.0951621\\
\hline
ccHours & 2391.667 & 0.0001320 & -0.7222674 & 1.0449378\\
\hline
hhTotal & 2391.965 & 0.0001205 & -0.8716164 & 0.9255789\\
\hline
hhSibs & 2392.245 & 0.0000189 & -1.0114203 & 0.9762202\\
\hline
sibsChildAged & 2392.407 & 0.0000134 & -1.0924575 & 1.0418509\\
\hline
ccAge & 2392.445 & 0.1182920 & -1.1114913 & 1.6858011\\
\hline
null & 2392.618 & 0.0000583 & -1.1978484 & 1.2901087\\
\hline
siblingsVarietyScoreW & 2392.952 & 0.0000064 & -1.3648559 & 1.0877168\\
\hline
\end{tabular}

>>>>

In addition, we recruited a remote adult sample by advertising the study on \emph{Prolific}. \emph{Prolific} is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of 50 and 50 English-speakers with an average age of 31.92 and 30.76 years (SD = 12.15 and 9.12, range = 18 and 19 - 63 and 59, 36 and 28 females).
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour). \emph{Prolific} distributed our study link to potential participants, while the hosting of the online study was done by local servers in the Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany.

@@

For our child sample, we went to kindergartens in Leipzig and surroundings.
The child sample consisted of
106 children, including
35 3-year-olds
(mean = 42.57 months,
SD = 2.98,
range = 38
- 47,
17 girls),
38 4-year-olds
(mean = 53.77 months,
SD = 3.16,
range = 48
- 59,
20 girls),
and 33 5-year-olds
(mean = 66.12 months,
SD = 3.36,
range = 61
- 71,
17 girls).

The adult sample was recruited over \emph{Prolific} and consisted of 70 and 66 English-speakers with an average age of 25.43 and 26.05 years (SD = 6.43 and 9.44, range = 18 and 18 - 51 and 71, 45 and 42 females).

@@

For this exploratory analysis, we included all children of the aforementioned samples where families filled out a short demographic questionnaire. This subsample consisted of
136 children, including
41 3-year-olds
(mean = 43.17 months,
SD = 3.13,
range = 37
- 47,
23 girls),
46 4-year-olds
(mean = 54.43 months,
SD = 2.76,
range = 48
- 59,
34 girls),
and 49 5-year-olds
(mean = 66.25 months,
SD = 3.47,
range = 60
- 71,
27 girls).

@@

On the trial level, the model including the verification of choice as a main effect won: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box. Interestingly, the effect reversed on a subject level - possibly due to greatest learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments. On the subject level, the model including number of repeated testquestions won: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box. In all cases, however, ELPD difference scores were smaller than their standard errors. Similarly, 95\% CI of the model estimates included zero and were rather wide (Table \ref{tab:webcam_table}). Therefore, we conclude that no stable effect of parental interference could be confirmed in this exploratory analysis.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:webcam_table}Model comparison for exploratory webcam coding of parental interference}

\begin{tabular}{lllll}
\toprule
model & \multicolumn{1}{c}{waic} & \multicolumn{1}{c}{waic\_weight} & \multicolumn{1}{c}{elpd\_diff} & \multicolumn{1}{c}{se\_diff}\\
\midrule
mPerTrialVerificationChoice & 263.24 & 0.65 & 0.00 & 0.00\\
mPerTrialNull & 263.75 & 0.35 & -0.25 & 1.20\\
mPerTrialPI & 264.35 & 0.00 & -0.55 & 0.98\\
mPerTrialRepeatedTestquestion & 265.43 & 0.00 & -1.10 & 1.27\\
mPerTrialHintsEyes & 265.67 & 0.00 & -1.21 & 1.26\\
mPerTrialParentSpeech & 266.45 & 0.00 & -1.61 & 1.21\\
mPerSubjectRepeatedTestquestion & 83.53 & 0.70 & 0.00 & 0.00\\
mPerSubjectPI & 88.25 & 0.00 & -2.36 & 3.60\\
mPerSubjectNull & 89.26 & 0.00 & -2.87 & 3.61\\
mPerSubjectVerificationChoice & 89.86 & 0.30 & -3.17 & 4.48\\
mPerSubjectParentSpeech & 90.45 & 0.00 & -3.46 & 4.20\\
mPerSubjectHintsEyes & 92.76 & 0.00 & -4.62 & 3.77\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} All models included random intercepts for participant and target position.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

@@

As can be seen, ELPD difference scores are smaller than their respective standard errors. WAIC scores between models don't differ substantially (Table \ref{tab:extvali_table}). All effects except when a child entered childcare positively influence performance.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:extvali_table}Model comparison for influences of children's social surrounding}

\begin{tabular}{lllll}
\toprule
model & \multicolumn{1}{c}{waic} & \multicolumn{1}{c}{waic\_weight} & \multicolumn{1}{c}{elpd\_diff} & \multicolumn{1}{c}{se\_diff}\\
\midrule
mPerTrialVerificationChoice & 263.24 & 0.65 & 0.00 & 0.00\\
mPerTrialNull & 263.75 & 0.35 & -0.25 & 1.20\\
mPerTrialPI & 264.35 & 0.00 & -0.55 & 0.98\\
mPerTrialRepeatedTestquestion & 265.43 & 0.00 & -1.10 & 1.27\\
mPerTrialHintsEyes & 265.67 & 0.00 & -1.21 & 1.26\\
mPerTrialParentSpeech & 266.45 & 0.00 & -1.61 & 1.21\\
mPerSubjectRepeatedTestquestion & 83.53 & 0.70 & 0.00 & 0.00\\
mPerSubjectPI & 88.25 & 0.00 & -2.36 & 3.60\\
mPerSubjectNull & 89.26 & 0.00 & -2.87 & 3.61\\
mPerSubjectVerificationChoice & 89.86 & 0.30 & -3.17 & 4.48\\
mPerSubjectParentSpeech & 90.45 & 0.00 & -3.46 & 4.20\\
mPerSubjectHintsEyes & 92.76 & 0.00 & -4.62 & 3.77\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} All models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}
